\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}
This literature research investigates 3 topics in robotics and combines them in a proposed solution to see if they complement and enhance each other. These topics are \textit{learning system models} with system identification techniques, \textit{task and motion planning} in an environment with movable obstacles and lastly \textit{manipulation} of objects to push them to target locations. After investigating existing solutions to these individual topics, existing literature which combines 3 of these 3 topics is researched and discussed. Multiple studies combine learning system models with \ac{NAMO}, but leave manipulation out of the scope, studies related to object manipulation are mostly combined with learning system models, and leave \ac{NAMO} out of the equation. The one study found combining both 3 topics uses an radically different approach compared to the proposed method in this literature. This allows to conclude that this literature enters new territory in the field of robotics, because the proposed method combines all 3 topics. The research question is similar to: can these 3 topics be combined? and reads: Can objects’ system models be learned by a robot during task execution, and can these newly learned models improve task, motion and manipulation planning? \\

A solution is proposed which combines the 3 topics and answers the research question. Even though the proposed solution still has to be verified, the individual research topics have been shown to be successful many times over. The robustness of backward induction reveals the possibility for converging toward  reliable, stable performance of completing tasks. 

\begin{flushright}
{\makeatletter\itshape
    \@author \\
    Delft, \monthname{} \the\year{}
\makeatother}
\end{flushright}
